---
title: "Time Spans"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(readr)
library(tidyverse)
```

First, the Emergency Response Incidents Dataset is loaded. 

```{r}
my_data <- read_csv("https://data.cityofnewyork.us/resource/pasr-j7fb.csv")
head(my_data)
```

First, I view the structure of the dataset.

```{r}
str(my_data)
```
The two date-time columns are creation_date and closed_date. These columns are type "POSIXct" by default. 

Since, this dataset is about Emergency Response times the time span should be minutes, hours or days. 

### Calculation time span:

When I subtract the two date-time columns the time span is returned in minutes by default. Then I convert the column datatype to a number. 
```{r}
my_data$response_time_span_min = (my_data$closed_date - my_data$creation_date)
my_data$response_time_span_min = as.numeric(my_data$response_time_span_min)
```

Next, I divided the time span in minutes by 60 (60 minutes in a hour) to find the time span in hours. 
```{r}
my_data$response_time_span_hours = my_data$response_time_span_min/60
```

Then, I divided the time span in hours by 24 (24 hours in a day) to find the time span in days.
```{r}
my_data$response_time_span_days = my_data$response_time_span_hours/24
```

Here is the structure of the dataset with the extra time span columns.
```{r}
my_data_no_missing = na.omit(my_data)
str(my_data_no_missing)
```